---
title: "Analysis"
author: "Genna Campain"
date: "2024-05-16"
output:
  pdf_document: default
  html_document: default
---
# Load Data and Libraries
```{r setup, message=FALSE, warning = FALSE}
library(dplyr)
# skewness function
library(e1071)
# coefficient plots
library(coefplot)
# set wd
cohort <- read.csv("~/Documents/GitHub/Assignment7/raw-data/cohort.csv") %>%
  select(smoke, female, cardiac, age, cost)
```

# Table Describing the Variables
Include mean, sd, min/max, and skewness for each variable
```{r}
varnames <- as.matrix(names(cohort), nrow = 5, ncol = 1)
meanmat <- matrix(data = 0, nrow = 5, ncol = 1)
sdmat <- matrix(data = 0, nrow = 5, ncol = 1)
minmaxmat <- matrix(data = NA, nrow = 5, ncol = 2)
skewmat <- matrix(data = NA, nrow = 5)
for(i in 1:5){
  meanmat[i] <- round(mean(cohort[,i]), digits = 5)
  sdmat[i] <- round(sd(cohort[,i]), digits = 5)
  minmaxmat[i,1] <- round(min(cohort[,i]), digits = 5)
  minmaxmat[i,2] <- round(max(cohort[,i]), digits = 5)
  skewmat[i] <- round(skewness(cohort[,i]), digits = 5)
}
table <- cbind(varnames, minmaxmat, meanmat, sdmat, skewmat)
colnames(table) <- list("Variable", "Min", "Max", "Mean", "SD", "Skewness")
as.data.frame(table)
```

# Regression-based Approach
Run regression
We don't have descriptions of what exactly the variables mean, but I am going to assume the following:
- "Cost" is the cost of a healthcare visit for the individual. This will be my dependent variable of interest.
- "Cardiac" indicates whether the individual has previously been seen for a cardiac-related complaint.
- "Smoke" indicates whether the person smokes regularily.
- "Female" and "Age" are self-explanatory.
I am interested in Cost ~ Cardiac + Smoke + Age + Female
```{r}
reg1 <- lm(cost ~ cardiac + smoke + age + female, data = cohort)
summary(reg1)
```

# Figure
```{r}
coeffig <- coefplot(reg1, 
                    title = "Coefficients for Linear Regression",
                    color = "Maroon")
coeffig
```





